quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-05 paper-quollr.Rmd
Updated the trimesh

```{r}
#| label: read-limb-nldr
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
clr_choice <- "#0077A3"
umap_limb <- read_rds("data/limb_muscles/facs_limb_muscles_umap_n-neigbors_15_min-dist_0.1.rds")

@@

>>>>

```{r}
#| label: read-limb-nldr
# Read a variety of different NLDR representations of limb
# and plot them on same aspect ratio
clr_choice <- "#0077A3"
umap_limb <- read_rds("data/limb_muscles/facs_limb_muscles_umap_n-neigbors_15_min-dist_0.1.rds")

@@

```{r}
#| label: data-limb

training_data_limb <- read_rds("data/limb_muscles/facs_limb_muscles_pcs_10.rds")
```

```{r}
#| label: tsne-num-bins-limb

## Compute hexbin parameters
num_bins_x_limb <- 16

algo_obj_limb <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_limb, 
  nldr_data = tsne_limb, 
  num_x_bins = num_bins_x_limb)

tsne_limb_scaled <- algo_obj_limb$nldr_scaled
distance_limb <- algo_obj_limb$distance_df
tr_from_to_df_limb <- algo_obj_limb$tr_from_to_df
benchmark_limb <- algo_obj_limb$benchmark
df_bin_centroids_limb <- algo_obj_limb$df_bin_centroids
df_bin_limb <- algo_obj_limb$df_bin

distance_df_small_edges_limb <- distance_limb |>
  filter(distance < benchmark_limb) #benchmark_limb

tr_from_to_df_limb <- right_join(
  tr_from_to_df_limb, distance_df_small_edges_limb,
  by = c("from", "to"))

# umap_limb_scaled_with_cluster <- umap_limb_scaled |>
#   mutate(cluster = umap_limb_scaled_with_cluster$cluster)

trimesh_removed_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled,
    aes(
      x = emb1,
      y = emb2
    ),
    alpha = 0.3,
    color = "#a65628"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  #scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

```{r}
#| label: tsne-best-num-bins-limb

## Compute hexbin parameters
num_bins_x_limb <- 13

algo_obj_limb <- gen_nldr_vis_algo_obj(
  high_d_data = training_data_limb, 
  nldr_data = tsne_limb2, 
  num_x_bins = num_bins_x_limb)

tsne_limb_scaled_best <- algo_obj_limb$nldr_scaled
distance_limb <- algo_obj_limb$distance_df
tr_from_to_df_limb <- algo_obj_limb$tr_from_to_df
benchmark_limb <- algo_obj_limb$benchmark
df_bin_centroids_limb <- algo_obj_limb$df_bin_centroids
df_bin_limb <- algo_obj_limb$df_bin

distance_df_small_edges_limb <- distance_limb |>
  filter(distance < benchmark_limb) #benchmark_limb

tr_from_to_df_limb <- right_join(
  tr_from_to_df_limb, distance_df_small_edges_limb,
  by = c("from", "to"))

# umap_limb_scaled_with_cluster <- umap_limb_scaled |>
#   mutate(cluster = umap_limb_scaled_with_cluster$cluster)

trimesh_removed_limb_best <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_best,
    aes(
      x = emb1,
      y = emb2
    ),
    alpha = 0.3,
    color = "#ff7f00"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  #scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

```{r}
trimesh_removed_limb + trimesh_removed_limb_best +
  plot_layout(ncol = 3)
```
